Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-04-22 manuscript.R2.tex
reply to reviews 2

\section{\texorpdfstring{The relationship between \emph{p}-values from
TOST and SGPV when confidence intervals are
symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV1-1.pdf}
\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black
line) and SGPV (grey line) across a range of observed sample means
(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
a sample size of 30 and a standard deviation of 2, illustrating that
when the TOST \emph{p}-value = 0.5, the SGPV = 0.5, when the TOST
\emph{p}-value is 0.975, 1-SGPV = 1, and when the TOST \emph{p}-value =
0.025, 1-SGPV = 0.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV2-1.pdf}
\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black
line) and 1-SGPV (grey line) across a range of observed sample means
(x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with
a sample size of 30 and a standard deviation of 2.}
\end{figure}

@@

\subsection{SGPV as a uniform measure of
overlap}\label{sgpv-as-a-uniform-measure-of-overlap}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV3-1.pdf}
\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for
three example datasets that illustrate the relationship between
\emph{p}-values from TOST and SGPV.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV4-1.pdf}
\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for
samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
\end{figure}

@@

\subsection{\texorpdfstring{When different \emph{p}-values for
equivalence tests yield the same
SGPV}{When different p-values for equivalence tests yield the same SGPV}}\label{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV5-1.pdf}
\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV1}.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV6-1.pdf}
\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black
line) and SGPV (grey line) across a range of observed sample means
(x-axis). Because the sample size is small (n = 10) and the CI is more
than twice as wide as the equivalence range (set to -0.4 to 0.4), the
SGPV is set to 0.5 (horizontal lightgrey line) across a range of
observed means.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV7-1.pdf}
\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV6}.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV8-1.pdf}
\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the
lower and upper equivalence bound (indicated by the vertical dotted
lines).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV9-1.pdf}
\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black
line) and SGPV (grey line) across a range of observed sample means
(x-axis). The sample size is small (n = 10), but because the sd is half
as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less
than twice as wide as the equivalence range (set to -0.4 to 0.4). The
SGPV is not set to 0.5 (horizontal light grey line) but reaches a
maximum slightly above 0.5 across a range of observed means.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV10-1.pdf}
\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from
the TOST procedure and the SGPV for the same scenario as in Figure
\ref{fig:TOSTSGPV9}.}
\end{figure}

@@

\subsection{The relation between equivalence tests and SGPV for
asymmetrical confidence intervals around
correlations}\label{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}

So far we have only looked at the relation between equivalence tests and
the SGPV when confidence intervals are symmetric (e.g., for confidence
intervals around mean differences). For correlations, which are bound
between -1 and 1, confidence intervals are only symmetric for a
correlation of exactly 0. The confidence interval for a correlation
becomes increasingly asymmetric as the observed correlation nears -1 or
1. For example, with ten observations, an observed correlation of 0 has
a symmetric 95\% confidence interval ranging from -0.630 to 0.630, while
and observed correlation of 0.7 has an asymmetric 95\% confidence
interval ranging from 0.126 to 0.993. Note that calculating confidence
intervals for a correlation involves a Fisher's z-transformation, which
transforms values such that they are approximately normally
z-distributed, which allows one to compute symmetric confidence
intervals. These confidence intervals are then retransformed into a
correlation, where the confidence intervals are asymmetric if the
correlation is not exactly zero.

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV11-1.pdf}
\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST
(black line) and 1-SGPV (grey curve) across a range of observed sample
correlations (x-axis) tested against equivalence bounds of r = -0.45 and
r = 0.45 with n = 30 and an alpha of 0.05.}
\end{figure}

The reason that the equivalence test and SGPV no longer overlap is also
because of asymmetric confidence intervals. If the observed correlation
falls exactly on the equivalence bound the \emph{p}-value for the
equivalence test indicates that the probability of observing the
observed or more extreme data, assuming the equivalence bound is the
true effect size, is 50\%. In other words, if the true effect size is
the same as the equivalence bound, it is equally likely to find an
effect more extreme than the equivalence bound, as it is to observe an
effect that is less extreme than the equivalence bound. However, as can
be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation
\emph{p}-values associated with the observed correlations at \emph{r} =
-0.45 and \emph{r} = 0.45 are larger than 50\%. Because the confidence
intervals are asymmetric around the observed effect size of 0.45
(ranging from 0.11 to 0.70) according to Blume et al. (2018) 58.11\% of
the data-supported hypotheses are null hypotheses, and therefore 58.10\%
of the data-supported hypotheses are compatible with the null premise.

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV12-1.pdf}
\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed
effect sizes of \emph{r} = -0.45, \emph{r} = 0, and \emph{r} = 0.45 for
n = 30. Only the confidence interval for \emph{r} = 0 is symmetric.}
\end{figure}

This example illustrates the difference between a proportion and a
probability. As long as data are sampled from a bivariate normal
distribution, there is always a 50\% probability of observing a
correlation smaller or larger than the true correlation, but the SGPV
for this situation depends on how far away the observed correlation is
from 0. The further away from 0, the larger the SGPV when the observed
mean falls on the equivalence bound. The SGPV is the proportion of
values in a 95\% confidence interval that overlap with the equivalence
range, but not the probability that these values will be observed. In
the most extreme case (i.e., a sample size of 4, and equivalence bounds
set to r = -0.99 and 0.99, with an observed correlation of 0.99) 58.10\%
of the confidence interval overlaps with the equivalence range, even
though in the long run only 50\% of the correlations observed in the
future will fall in this range. It should be noted that in larger sample
sizes the SGPV is closer to 0.5 whenever the observed correlation falls
on the equivalence bound, but this extreme example nevertheless clearly
illustrates the difference between question the SGPV answers, and the
question a \emph{p}-value answers. The conclusion of this section on
asymmetric confidence intervals is that a SGPV of 1 or 0 can still be
interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{}
0.975 in an equivalence test, since the SGPV and \emph{p}-value for the
TOST procedure are always directly related at the values \emph{p} =
0.025 and \emph{p} = 0.975. Although Blume et al. (2018) state that
\enquote{the degree of overlap conveys how compatible the data are with
the null premise} this definition of what the SGPV provides does not
hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can
be directly interpreted, a SGPV between 0 and 1 is not interpretable as
\enquote{compatibility with the null hypothesis} under the assumption of
a bivariate normal distribution, and the generalizability of this
statement needs to be examined beyond normal bivariate distributions.
Indeed, Blume and colleagues write in the supplemental material that
\enquote{The magnitude of an inconclusive second-generation
\emph{p}-value can vary slightly when the effect size scale is
transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or
1 are \emph{not} affected by the scale changes.}

\subsection{What are the Relative Strengths and Weaknesses of
Equivalence Testing and the
SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R1_files/figure-latex/TOSTSGPV13-1.pdf}
\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST
(black line) and 1-SGPV (grey curve) across a range of observed sample
correlations (x-axis) tested against equivalence bounds of \emph{r} =
0.4 and \emph{r} = 0.8 with n = 10 and an alpha of 0.05.}
\end{figure}

@@

\section{Conclusion}\label{conclusion}

@@

\hypertarget{refs}{}
\hypertarget{ref-american_psychological_association_publication_2010}{}
American Psychological Association (Ed.). (2010). \emph{Publication
manual of the American Psychological Association} (6th ed.). Washington,
DC: American Psychological Association.

\hypertarget{ref-blume_second-generation_2018}{}
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
(2018). Second-generation p-values: Improved rigor, reproducibility, \&
transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
e0188299.
doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\hypertarget{ref-hauck_new_1984}{}
Hauck, D. W. W., \& Anderson, S. (1984). A new statistical procedure for
testing equivalence in two-group comparative bioavailability trials.
\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1),
83--91.
doi:\href{https://doi.org/10.1007/BF01063612}{10.1007/BF01063612}

\hypertarget{ref-kruschke_rejecting_2018}{}
Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in
Bayesian Estimation. \emph{Advances in Methods and Practices in
Psychological Science}, 2515245918771304.
doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}

\hypertarget{ref-lakens_equivalence_2017}{}
Lakens, D. (2017). Equivalence Tests: A Practical Primer for t Tests,
Correlations, and Meta-Analyses. \emph{Social Psychological and
Personality Science}, \emph{8}(4), 355--362.
doi:\href{https://doi.org/10.1177/1948550617697177}{10.1177/1948550617697177}

\hypertarget{ref-lakens_equivalence_2018}{}
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing
for Psychological Research: A Tutorial. \emph{Advances in Methods and
Practices in Psychological Science}, 2515245918770963.
doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}

\hypertarget{ref-meyners_equivalence_2012}{}
Meyners, M. (2012). Equivalence tests review. \emph{Food Quality and
Preference}, \emph{26}(2), 231--245.
doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}

\hypertarget{ref-murphy_statistical_2014}{}
Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
power analysis: A simple and general model for traditional and modern
hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
Francis Group.

\hypertarget{ref-quertemont_how_2011}{}
Quertemont, E. (2011). How to Statistically Show the Absence of an
Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127.
doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}

\hypertarget{ref-rogers_using_1993}{}
Rogers, J. L., Howard, K. I., \& Vessey, J. T. (1993). Using
significance tests to evaluate equivalence between two experimental
groups. \emph{Psychological Bulletin}, \emph{113}(3), 553--565.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/0033-2909.113.3.553}{http://dx.doi.org/10.1037/0033-2909.113.3.553}

\hypertarget{ref-schuirmann_comparison_1987}{}
Schuirmann, D. J. (1987). A comparison of the two one-sided tests
procedure and the power approach for assessing the equivalence of
average bioavailability. \emph{Journal of Pharmacokinetics and
Biopharmaceutics}, \emph{15}(6), 657--680.

\hypertarget{ref-serlin_rationality_1985}{}
Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological
research: The good-enough principle.

\hypertarget{ref-spiegelhalter_bayesian_1994}{}
Spiegelhalter, D. J., Freedman, L. S., \& Parmar, M. K. (1994). Bayesian
approaches to randomized trials. \emph{Journal of the Royal Statistical
Society. Series A (Statistics in Society)}, 357--416.
doi:\href{https://doi.org/10.2307/2983527}{10.2307/2983527}

\hypertarget{ref-wellek_testing_2010}{}
Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence
and noninferiority} (2nd ed.). Boca Raton: CRC Press.

\hypertarget{ref-westlake_use_1972}{}
Westlake, W. J. (1972). Use of Confidence Intervals in Analysis of
Comparative Bioavailability Trials. \emph{Journal of Pharmaceutical
Sciences}, \emph{61}(8), 1340--1341.
doi:\href{https://doi.org/10.1002/JPS.2600610845}{10.1002/JPS.2600610845}

>>>>

\hypertarget{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}{%
\section{\texorpdfstring{The relationship between \emph{p}-values from TOST and SGPV when confidence intervals are symmetrical}{The relationship between p-values from TOST and SGPV when confidence intervals are symmetrical}}\label{the-relationship-between-p-values-from-tost-and-sgpv-when-confidence-intervals-are-symmetrical}}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV1-1.pdf}
\caption{\label{fig:TOSTSGPV1}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2, illustrating that when the TOST \emph{p}-value = 0.5, the SGPV = 0.5, when the TOST \emph{p}-value is 0.975, 1-SGPV = 1, and when the TOST \emph{p}-value = 0.025, 1-SGPV = 0.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV2-1.pdf}
\caption{\label{fig:TOSTSGPV2}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey line) across a range of observed sample means (x-axis) tested against a mean of 145 in a one-sample \emph{t}-test with a sample size of 30 and a standard deviation of 2.}
\end{figure}

@@

\hypertarget{sgpv-as-a-uniform-measure-of-overlap}{%
\subsection{SGPV as a uniform measure of overlap}\label{sgpv-as-a-uniform-measure-of-overlap}}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV3-1.pdf}
\caption{\label{fig:TOSTSGPV3}Means, normal distribution, and 95\% CI for three example datasets that illustrate the relationship between \emph{p}-values from TOST and SGPV.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV4-1.pdf}
\caption{\label{fig:TOSTSGPV4}Means, normal distribution, and 95\% CI for samples where the observed population mean is 1.5, 1.4, 1.3, and 1.2.}
\end{figure}

@@

\hypertarget{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}{%
\subsection{\texorpdfstring{When different \emph{p}-values for equivalence tests yield the same SGPV}{When different p-values for equivalence tests yield the same SGPV}}\label{when-different-p-values-for-equivalence-tests-yield-the-same-sgpv}}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV5-1.pdf}
\caption{\label{fig:TOSTSGPV5}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV1}.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV6-1.pdf}
\caption{\label{fig:TOSTSGPV6}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis). Because the sample size is small (n = 10) and the CI is more than twice as wide as the equivalence range (set to -0.4 to 0.4), the SGPV is set to 0.5 (horizontal lightgrey line) across a range of observed means.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV7-1.pdf}
\caption{\label{fig:TOSTSGPV7}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV6}.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV8-1.pdf}
\caption{\label{fig:TOSTSGPV8}Example of a 95\% CI that overlaps with the lower and upper equivalence bound (indicated by the vertical dotted lines).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV9-1.pdf}
\caption{\label{fig:TOSTSGPV9}Comparison of \emph{p}-values from TOST (black line) and SGPV (grey line) across a range of observed sample means (x-axis). The sample size is small (n = 10), but because the sd is half as big as in Figure \ref{fig:TOSTSGPV7} (1 instead of 2) the CI is less than twice as wide as the equivalence range (set to -0.4 to 0.4). The SGPV is not set to 0.5 (horizontal light grey line) but reaches a maximum slightly above 0.5 across a range of observed means.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV10-1.pdf}
\caption{\label{fig:TOSTSGPV10}The relationship between \emph{p}-values from the TOST procedure and the SGPV for the same scenario as in Figure \ref{fig:TOSTSGPV9}.}
\end{figure}

@@

\hypertarget{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}{%
\subsection{The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations}\label{the-relation-between-equivalence-tests-and-sgpv-for-asymmetrical-confidence-intervals-around-correlations}}

So far we have only looked at the relation between equivalence tests and the SGPV when confidence intervals are symmetric (e.g., for confidence intervals around mean differences). For correlations, which are bound between -1 and 1, confidence intervals are only symmetric for a correlation of exactly 0. The confidence interval for a correlation becomes increasingly asymmetric as the observed correlation nears -1 or 1. For example, with ten observations, an observed correlation of 0 has a symmetric 95\% confidence interval ranging from -0.63 to 0.63, while and observed correlation of 0.7 has an asymmetric 95\% confidence interval ranging from 0.13 to 0.92. Note that calculating confidence intervals for a correlation involves a Fisher's z-transformation, which transforms values such that they are approximately normally z-distributed, which allows one to compute symmetric confidence intervals. These confidence intervals are then retransformed into a correlation, where the confidence intervals are asymmetric if the correlation is not exactly zero.

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV11-1.pdf}
\caption{\label{fig:TOSTSGPV11}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of r = -0.45 and r = 0.45 with n = 30 and an alpha of 0.05.}
\end{figure}

The reason that the equivalence test and SGPV no longer overlap is due to asymmetric confidence intervals. If the observed correlation falls exactly on the equivalence bound the \emph{p}-value for the equivalence test is 0.5. In the equivalence test for correlations the \emph{p} value is computed based on a z-transformation which better controls error rates (Goertzen \& Cribbie, 2010). This transformation is computed as follows, where \emph{r} is the observed correlation and \(\rho\) is the theoretical correlation under the null:

\[
z = \frac{\frac{\log(\frac{1 + r}{ 1 - r})}{2} - \frac{\log(\frac{1 + \rho}{ 1 - \rho})}{2}}{\sqrt{\frac{1}{n-3}}}
\]

Because the z-distribution is symmetric, the probability of observing the observed or more extreme z-score, assuming the equivalence bound is the true effect size, is 50\%. However, because the \emph{r} distribution is not symmetric, this does not mean that there is always a 50\% probability of observing a correlation smaller or larger than the true correlation. As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at \emph{r} = -0.45 and \emph{r} = 0.45 are larger than 50\%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.11 to 0.70) according to Blume et al. (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.11\% of the data-supported hypotheses are compatible with the null premise.

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV12-1.pdf}
\caption{\label{fig:TOSTSGPV12}Three 95\% confidence intervals for observed effect sizes of \emph{r} = -0.45, \emph{r} = 0, and \emph{r} = 0.45 for n = 30. Only the confidence interval for \emph{r} = 0 is symmetric.}
\end{figure}

This example illustrates the difference between a proportion and a probability. As long as data are sampled from a bivariate normal distribution, there is always a 50\% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 36\% of the correlations observed in the future will fall in this range.

It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between question the SGPV answers, and the question a \emph{p}-value answers. The conclusion of this section on asymmetric confidence intervals is that a SGPV of 1 or 0 can still be interpreted as a \emph{p} \textless{} 0.025 or \emph{p} \textgreater{} 0.975 in an equivalence test, since the SGPV and \emph{p}-value for the TOST procedure are always directly related at the values \emph{p} = 0.025 and \emph{p} = 0.975. Although Blume et al. (2018) state that \enquote{the degree of overlap conveys how compatible the data are with the null premise} this definition of what the SGPV provides does not hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as \enquote{compatibility with the null hypothesis} under the assumption of a bivariate normal distribution, and the generalizability of this statement needs to be examined beyond normal bivariate distributions. Indeed, Blume and colleagues write in the supplemental material that \enquote{The magnitude of an inconclusive second-generation \emph{p}-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale changes.}

\hypertarget{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}{%
\subsection{What are the Relative Strengths and Weaknesses of Equivalence Testing and the SGPV?}\label{what-are-the-relative-strengths-and-weaknesses-of-equivalence-testing-and-the-sgpv}}

@@

\begin{figure}
\centering
\includegraphics{manuscript.R2_files/figure-latex/TOSTSGPV13-1.pdf}
\caption{\label{fig:TOSTSGPV13}Comparison of \emph{p}-values from TOST (black line) and 1-SGPV (grey curve) across a range of observed sample correlations (x-axis) tested against equivalence bounds of \emph{r} = 0.4 and \emph{r} = 0.8 with n = 10 and an alpha of 0.05.}
\end{figure}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-american_psychological_association_publication_2010}{}%
American Psychological Association (Ed.). (2010). \emph{Publication manual of the American Psychological Association} (6th ed.). Washington, DC: American Psychological Association.

\leavevmode\hypertarget{ref-blume_second-generation_2018}{}%
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A. (2018). Second-generation p-values: Improved rigor, reproducibility, \& transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3), e0188299. doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\leavevmode\hypertarget{ref-goertzen_detecting_2010}{}%
Goertzen, J. R., \& Cribbie, R. A. (2010). Detecting a lack of association: An equivalence testing approach. \emph{British Journal of Mathematical and Statistical Psychology}, \emph{63}(3), 527--537. doi:\href{https://doi.org/10.1348/000711009X475853}{10.1348/000711009X475853}

\leavevmode\hypertarget{ref-hauck_new_1984}{}%
Hauck, D. W. W., \& Anderson, S. (1984). A new statistical procedure for testing equivalence in two-group comparative bioavailability trials. \emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{12}(1), 83--91. doi:\href{https://doi.org/10.1007/BF01063612}{10.1007/BF01063612}

\leavevmode\hypertarget{ref-kruschke_rejecting_2018}{}%
Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in Bayesian Estimation. \emph{Advances in Methods and Practices in Psychological Science}, 2515245918771304. doi:\href{https://doi.org/10.1177/2515245918771304}{10.1177/2515245918771304}

\leavevmode\hypertarget{ref-lakens_equivalence_2017}{}%
Lakens, D. (2017). Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. doi:\href{https://doi.org/10.1177/1948550617697177}{10.1177/1948550617697177}

\leavevmode\hypertarget{ref-lakens_equivalence_2018}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, 2515245918770963. doi:\href{https://doi.org/10.1177/2515245918770963}{10.1177/2515245918770963}

\leavevmode\hypertarget{ref-meyners_equivalence_2012}{}%
Meyners, M. (2012). Equivalence tests A review. \emph{Food Quality and Preference}, \emph{26}(2), 231--245. doi:\href{https://doi.org/10.1016/j.foodqual.2012.05.003}{10.1016/j.foodqual.2012.05.003}

\leavevmode\hypertarget{ref-murphy_statistical_2014}{}%
Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical power analysis: A simple and general model for traditional and modern hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \& Francis Group.

\leavevmode\hypertarget{ref-quertemont_how_2011}{}%
Quertemont, E. (2011). How to Statistically Show the Absence of an Effect. \emph{Psychologica Belgica}, \emph{51}(2), 109--127. doi:\href{https://doi.org/10.5334/pb-51-2-109}{10.5334/pb-51-2-109}

\leavevmode\hypertarget{ref-rogers_using_1993}{}%
Rogers, J. L., Howard, K. I., \& Vessey, J. T. (1993). Using significance tests to evaluate equivalence between two experimental groups. \emph{Psychological Bulletin}, \emph{113}(3), 553--565. doi:\href{https://doi.org/http://dx.doi.org/10.1037/0033-2909.113.3.553}{http://dx.doi.org/10.1037/0033-2909.113.3.553}

\leavevmode\hypertarget{ref-schuirmann_comparison_1987}{}%
Schuirmann, D. J. (1987). A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability. \emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.

\leavevmode\hypertarget{ref-serlin_rationality_1985}{}%
Serlin, R. C., \& Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.

\leavevmode\hypertarget{ref-spiegelhalter_bayesian_1994}{}%
Spiegelhalter, D. J., Freedman, L. S., \& Parmar, M. K. (1994). Bayesian approaches to randomized trials. \emph{Journal of the Royal Statistical Society. Series A (Statistics in Society)}, 357--416. doi:\href{https://doi.org/10.2307/2983527}{10.2307/2983527}

\leavevmode\hypertarget{ref-wellek_testing_2010}{}%
Wellek, S. (2010). \emph{Testing statistical hypotheses of equivalence and noninferiority} (2nd ed.). Boca Raton: CRC Press.

\leavevmode\hypertarget{ref-westlake_use_1972}{}%
Westlake, W. J. (1972). Use of Confidence Intervals in Analysis of Comparative Bioavailability Trials. \emph{Journal of Pharmaceutical Sciences}, \emph{61}(8), 1340--1341. doi:\href{https://doi.org/10.1002/JPS.2600610845}{10.1002/JPS.2600610845}
